Supplementary material for ``Current status and prospects of R-packages for the design of experiments''

### 2022-12-13 supp.tex
huge update for index with cleaner pipeline

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Supplementary material for ``Current status and prospects of R-packages for the design of experiments''},
  pdfauthor={Emi Tanaka; Dewi Amaliah},
  pdfkeywords={experimental design, CRAN task view, user interface},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{colortbl}
\usepackage{bera}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage[utf8]{inputenc}
\usepackage{caption}
\renewcommand{\figurename}{Figure S}
\makeatletter
\def\fnum@figure{\figurename\thefigure}
\makeatother
\renewcommand{\tablename}{Table S}
\makeatletter
\def\fnum@table{\tablename\thetable}
\makeatother

\usepackage{bera}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{biblatex}
\addbibresource{pkgs.bib}

@@

\cellcolor{gray!6}{ExperimentalDesign} & \cellcolor{gray!6}{Design of Experiments (DoE) \& Analysis of Experimental Data} & \cellcolor{gray!6}{112} & \cellcolor{gray!6}{211} & \cellcolor{gray!6}{2.27} & \cellcolor{gray!6}{29}\\
SportsAnalytics & Sports Analytics & 78 & 149 & 2.32 & 17\\
\cellcolor{gray!6}{MedicalImaging} & \cellcolor{gray!6}{Medical Image Analysis} & \cellcolor{gray!6}{32} & \cellcolor{gray!6}{53} & \cellcolor{gray!6}{2.44} & \cellcolor{gray!6}{44}\\
MetaAnalysis & Meta-Analysis & 157 & 351 & 2.63 & 43\\
\cellcolor{gray!6}{ChemPhys} & \cellcolor{gray!6}{Chemometrics and Computational Physics} & \cellcolor{gray!6}{75} & \cellcolor{gray!6}{162} & \cellcolor{gray!6}{2.65} & \cellcolor{gray!6}{28}\\

@@

ClinicalTrials & Clinical Trial Design, Monitoring, and Analysis & 59 & 141 & 2.76 & 31\\
\cellcolor{gray!6}{Distributions} & \cellcolor{gray!6}{Probability Distributions} & \cellcolor{gray!6}{257} & \cellcolor{gray!6}{597} & \cellcolor{gray!6}{2.88} & \cellcolor{gray!6}{45}\\
Survival & Survival Analysis & 239 & 558 & 2.92 & 73\\
\cellcolor{gray!6}{ExtremeValue} & \cellcolor{gray!6}{Extreme Value Analysis} & \cellcolor{gray!6}{37} & \cellcolor{gray!6}{89} & \cellcolor{gray!6}{2.95} & \cellcolor{gray!6}{41}\\
Optimization & Optimization and Mathematical Programming & 136 & 328 & 3.04 & 29\\

@@

\cellcolor{gray!6}{TimeSeries} & \cellcolor{gray!6}{Time Series Analysis} & \cellcolor{gray!6}{339} & \cellcolor{gray!6}{793} & \cellcolor{gray!6}{3.04} & \cellcolor{gray!6}{58}\\
OfficialStatistics & Official Statistics \& Survey Statistics & 131 & 325 & 3.06 & 40\\
\cellcolor{gray!6}{Hydrology} & \cellcolor{gray!6}{Hydrological Data and Modeling} & \cellcolor{gray!6}{100} & \cellcolor{gray!6}{252} & \cellcolor{gray!6}{3.09} & \cellcolor{gray!6}{24}\\
NumericalMathematics & Numerical Mathematics & 115 & 271 & 3.14 & 63\\
\cellcolor{gray!6}{Databases} & \cellcolor{gray!6}{Databases with R} & \cellcolor{gray!6}{43} & \cellcolor{gray!6}{95} & \cellcolor{gray!6}{3.23} & \cellcolor{gray!6}{77}\\

@@

WebTechnologies & Web Technologies and Services & 201 & 428 & 3.25 & 90\\
\cellcolor{gray!6}{NaturalLanguageProcessing} & \cellcolor{gray!6}{Natural Language Processing} & \cellcolor{gray!6}{56} & \cellcolor{gray!6}{130} & \cellcolor{gray!6}{3.30} & \cellcolor{gray!6}{62}\\
Bayesian & Bayesian Inference & 213 & 621 & 3.35 & 49\\
\cellcolor{gray!6}{FunctionalData} & \cellcolor{gray!6}{Functional Data Analysis} & \cellcolor{gray!6}{40} & \cellcolor{gray!6}{109} & \cellcolor{gray!6}{3.38} & \cellcolor{gray!6}{60}\\
Robust & Robust Statistical Methods & 59 & 136 & 3.41 & 75\\

@@

\cellcolor{gray!6}{Psychometrics} & \cellcolor{gray!6}{Psychometric Models and Methods} & \cellcolor{gray!6}{230} & \cellcolor{gray!6}{567} & \cellcolor{gray!6}{3.41} & \cellcolor{gray!6}{69}\\
Tracking & Processing and Analysis of Tracking Data & 46 & 149 & 3.46 & 48\\
\cellcolor{gray!6}{Cluster} & \cellcolor{gray!6}{Cluster Analysis \& Finite Mixture Models} & \cellcolor{gray!6}{108} & \cellcolor{gray!6}{305} & \cellcolor{gray!6}{3.47} & \cellcolor{gray!6}{39}\\
Econometrics & Econometrics & 152 & 363 & 3.50 & 81\\
\cellcolor{gray!6}{Finance} & \cellcolor{gray!6}{Empirical Finance} & \cellcolor{gray!6}{158} & \cellcolor{gray!6}{426} & \cellcolor{gray!6}{3.61} & \cellcolor{gray!6}{57}\\

@@

MissingData & Missing Data & 210 & 740 & 3.99 & 42\\
\cellcolor{gray!6}{SpatioTemporal} & \cellcolor{gray!6}{Handling and Analyzing Spatio-Temporal Data} & \cellcolor{gray!6}{81} & \cellcolor{gray!6}{269} & \cellcolor{gray!6}{4.04} & \cellcolor{gray!6}{70}\\
Spatial & Analysis of Spatial Data & 197 & 618 & 4.26 & 83\\
\cellcolor{gray!6}{GraphicalModels} & \cellcolor{gray!6}{Graphical Models} & \cellcolor{gray!6}{32} & \cellcolor{gray!6}{109} & \cellcolor{gray!6}{4.38} & \cellcolor{gray!6}{78}\\
Pharmacokinetics & Analysis of Pharmacokinetic Data & 29 & 109 & 4.55 & 21\\

@@

\cellcolor{gray!6}{HighPerformanceComputing} & \cellcolor{gray!6}{High-Performance and Parallel Computing with R} & \cellcolor{gray!6}{83} & \cellcolor{gray!6}{315} & \cellcolor{gray!6}{4.75} & \cellcolor{gray!6}{63}\\
DifferentialEquations & Differential Equations & 27 & 114 & 4.96 & 56\\
\cellcolor{gray!6}{Environmetrics} & \cellcolor{gray!6}{Analysis of Ecological and Environmental Data} & \cellcolor{gray!6}{93} & \cellcolor{gray!6}{383} & \cellcolor{gray!6}{5.02} & \cellcolor{gray!6}{74}\\
MachineLearning & Machine Learning \& Statistical Learning & 102 & 488 & 5.63 & 50\\
\cellcolor{gray!6}{TeachingStatistics} & \cellcolor{gray!6}{Teaching Statistics} & \cellcolor{gray!6}{46} & \cellcolor{gray!6}{236} & \cellcolor{gray!6}{6.35} & \cellcolor{gray!6}{57}\\

@@

ReproducibleResearch & Reproducible Research & 102 & 524 & 6.49 & 76\\
\cellcolor{gray!6}{ModelDeployment} & \cellcolor{gray!6}{Model Deployment with R} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{146} & \cellcolor{gray!6}{6.55} & \cellcolor{gray!6}{74}\\*

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{colortbl}
\usepackage{bera}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage[utf8]{inputenc}
\usepackage{caption}
\renewcommand{\figurename}{Figure S}
\makeatletter
\def\fnum@figure{\figurename\thefigure}
\makeatother
\renewcommand{\tablename}{Table S}
\makeatletter
\def\fnum@table{\tablename\thetable}
\makeatother

\usepackage{bera}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{biblatex}
\addbibresource{pkgs.bib}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Supplementary material for ``Current status and prospects of R-packages for the design of experiments''},
  pdfauthor={Emi Tanaka; Dewi Amaliah},
  pdfkeywords={experimental design, CRAN task view, user interface},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\cellcolor{gray!6}{ExperimentalDesign} & \cellcolor{gray!6}{Design of Experiments (DoE) \& Analysis of Experimental Data} & \cellcolor{gray!6}{105} & \cellcolor{gray!6}{192} & \cellcolor{gray!6}{2.23} & \cellcolor{gray!6}{30}\\
SportsAnalytics & Sports Analytics & 87 & 160 & 2.25 & 16\\
\cellcolor{gray!6}{MedicalImaging} & \cellcolor{gray!6}{Medical Image Analysis} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{48} & \cellcolor{gray!6}{2.32} & \cellcolor{gray!6}{45}\\
ChemPhys & Chemometrics and Computational Physics & 73 & 144 & 2.45 & 25\\
\cellcolor{gray!6}{ClinicalTrials} & \cellcolor{gray!6}{Clinical Trial Design, Monitoring, and Analysis} & \cellcolor{gray!6}{55} & \cellcolor{gray!6}{121} & \cellcolor{gray!6}{2.58} & \cellcolor{gray!6}{33}\\

@@

MetaAnalysis & Meta-Analysis & 153 & 338 & 2.59 & 44\\
\cellcolor{gray!6}{Distributions} & \cellcolor{gray!6}{Probability Distributions} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{580} & \cellcolor{gray!6}{2.88} & \cellcolor{gray!6}{46}\\
Survival & Survival Analysis & 234 & 556 & 2.95 & 71\\
\cellcolor{gray!6}{ExtremeValue} & \cellcolor{gray!6}{Extreme Value Analysis} & \cellcolor{gray!6}{37} & \cellcolor{gray!6}{89} & \cellcolor{gray!6}{2.97} & \cellcolor{gray!6}{41}\\
Hydrology & Hydrological Data and Modeling & 96 & 236 & 3.03 & 20\\

@@

\cellcolor{gray!6}{Optimization} & \cellcolor{gray!6}{Optimization and Mathematical Programming} & \cellcolor{gray!6}{136} & \cellcolor{gray!6}{329} & \cellcolor{gray!6}{3.04} & \cellcolor{gray!6}{29}\\
Pharmacokinetics & Analysis of Pharmacokinetic Data & 27 & 72 & 3.04 & 19\\
\cellcolor{gray!6}{TimeSeries} & \cellcolor{gray!6}{Time Series Analysis} & \cellcolor{gray!6}{333} & \cellcolor{gray!6}{791} & \cellcolor{gray!6}{3.08} & \cellcolor{gray!6}{57}\\
OfficialStatistics & Official Statistics \& Survey Statistics & 129 & 328 & 3.11 & 38\\
\cellcolor{gray!6}{NumericalMathematics} & \cellcolor{gray!6}{Numerical Mathematics} & \cellcolor{gray!6}{115} & \cellcolor{gray!6}{273} & \cellcolor{gray!6}{3.14} & \cellcolor{gray!6}{63}\\

@@

DifferentialEquations & Differential Equations & 26 & 71 & 3.27 & 54\\
\cellcolor{gray!6}{Bayesian} & \cellcolor{gray!6}{Bayesian Inference} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{589} & \cellcolor{gray!6}{3.29} & \cellcolor{gray!6}{49}\\
WebTechnologies & Web Technologies and Services & 197 & 429 & 3.30 & 87\\
\cellcolor{gray!6}{Tracking} & \cellcolor{gray!6}{Processing and Analysis of Tracking Data} & \cellcolor{gray!6}{47} & \cellcolor{gray!6}{146} & \cellcolor{gray!6}{3.34} & \cellcolor{gray!6}{45}\\
Databases & Databases with R & 41 & 94 & 3.34 & 78\\

@@

\cellcolor{gray!6}{NaturalLanguageProcessing} & \cellcolor{gray!6}{Natural Language Processing} & \cellcolor{gray!6}{55} & \cellcolor{gray!6}{129} & \cellcolor{gray!6}{3.35} & \cellcolor{gray!6}{62}\\
CausalInference & Causal Inference & 156 & 439 & 3.35 & 24\\
\cellcolor{gray!6}{Psychometrics} & \cellcolor{gray!6}{Psychometric Models and Methods} & \cellcolor{gray!6}{225} & \cellcolor{gray!6}{561} & \cellcolor{gray!6}{3.46} & \cellcolor{gray!6}{70}\\
Robust & Robust Statistical Methods & 56 & 129 & 3.46 & 75\\
\cellcolor{gray!6}{Cluster} & \cellcolor{gray!6}{Cluster Analysis \& Finite Mixture Models} & \cellcolor{gray!6}{106} & \cellcolor{gray!6}{303} & \cellcolor{gray!6}{3.50} & \cellcolor{gray!6}{39}\\

@@

Econometrics & Econometrics & 150 & 387 & 3.67 & 84\\
\cellcolor{gray!6}{Finance} & \cellcolor{gray!6}{Empirical Finance} & \cellcolor{gray!6}{154} & \cellcolor{gray!6}{438} & \cellcolor{gray!6}{3.85} & \cellcolor{gray!6}{57}\\
FunctionalData & Functional Data Analysis & 39 & 130 & 3.97 & 59\\
\cellcolor{gray!6}{MissingData} & \cellcolor{gray!6}{Missing Data} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{735} & \cellcolor{gray!6}{4.00} & \cellcolor{gray!6}{42}\\
Epidemiology & Epidemiology & 76 & 264 & 4.24 & 55\\

@@

\cellcolor{gray!6}{SpatioTemporal} & \cellcolor{gray!6}{Handling and Analyzing Spatio-Temporal Data} & \cellcolor{gray!6}{74} & \cellcolor{gray!6}{258} & \cellcolor{gray!6}{4.27} & \cellcolor{gray!6}{72}\\
Spatial & Analysis of Spatial Data & 192 & 608 & 4.32 & 82\\
\cellcolor{gray!6}{GraphicalModels} & \cellcolor{gray!6}{Graphical Models} & \cellcolor{gray!6}{31} & \cellcolor{gray!6}{108} & \cellcolor{gray!6}{4.48} & \cellcolor{gray!6}{81}\\
HighPerformanceComputing & High-Performance and Parallel Computing with R & 86 & 315 & 4.64 & 62\\
\cellcolor{gray!6}{Environmetrics} & \cellcolor{gray!6}{Analysis of Ecological and Environmental Data} & \cellcolor{gray!6}{92} & \cellcolor{gray!6}{386} & \cellcolor{gray!6}{5.11} & \cellcolor{gray!6}{74}\\

@@

MachineLearning & Machine Learning \& Statistical Learning & 101 & 494 & 5.73 & 50\\
\cellcolor{gray!6}{TeachingStatistics} & \cellcolor{gray!6}{Teaching Statistics} & \cellcolor{gray!6}{45} & \cellcolor{gray!6}{237} & \cellcolor{gray!6}{6.51} & \cellcolor{gray!6}{58}\\
ModelDeployment & Model Deployment with R & 31 & 146 & 6.58 & 74\\
\cellcolor{gray!6}{ReproducibleResearch} & \cellcolor{gray!6}{Reproducible Research} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{540} & \cellcolor{gray!6}{6.72} & \cellcolor{gray!6}{76}\\*

@@

!6\}\{ReproducibleResearch\} \& \cellcolor{gray!6}{Reproducible Research} \& \cellcolor{gray!6}{101} \& \cellcolor{gray!6}{540} \& \cellcolor{gray!6}{6.72} \& \cellcolor{gray!6}{76}\textbackslash*
\textbackslash end\{longtable\}
